PACE Solver Description: OCMu64,\\ a solver for One-sided Crossing Minimization

### 2024-09-20 tex/paper.tex
shrink to 4 pages

Let us also mention this gluing-like reduction: \emph{gluing to the front}, implied by RRL01 of
\cite{dujmovic_2008}.
\begin{lemma}[Greedy]\label{greedy}
  When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
  starts with $u$.
\end{lemma}

@@

\newpage

>>>>

Let us also mention this gluing-like reduction: \emph{gluing to the front}, implied by
\cite[RRL01]{dujmovic_2008}.
\begin{lemma}[Greedy]\label{greedy}
  \!\!When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
  starts with $u$.\!\!
\end{lemma}

@@
